\textls[-0]{\thetitle}

### 2023-03-23 metatheory2.tex
tweaks
Working on adding explanation of boldP

% Deal with intuition

@@

\subsection{A Translation that Compiles Away Linkages}

>>>>

% Deal with intuition
\noindentparagraph{The necessity of $\TyTkg{\cdot}$.} 
According to the equality rules of $\ruleref{}$, for a fixed $\lsig$, $\TyTkg{\lsig}$ is very similar to $\TyLkg{\lsig}$ but we are using dependent pair $\pair{}{}$ instead of $ $ to package the fields of a linkage. We can compute a concrete example to persuade the audience.

Thus the mystery of $\TyTkg{\cdot}$ really lies in its necessity. $\TyTkg{\cdot}$ is indispensible because we cannot do \emph{abstraction} with $\TyLkg{\cdot}$ alone, which in turn is due to the fact that an abstraction $A$ inside $\ruleref{}$ is usually a dependent tuple type. We make a small example here.

@@

\subsection{A Translation that Compiles Linkages Away}
